Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-02-28 progressPresentation.tex
Updated references, progressPresentation, and added result figures

\begin{frame}{Introduction}{}
    \begin{block}{}
    	\begin{itemize}
    		\item 
		\end{itemize}
    \end{block}

@@

\begin{frame}{Steering Subsystem}
  \begin{block}{}
 \begin{itemize}
        \item 
	\end{itemize}

@@

\begin{frame}{Acceleration Subsystem}
  \begin{block}{}
 \begin{itemize}
        \item 
	\end{itemize}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Semester goals}
    %\begin{LARGE}
      \begin{itemize}
        \item 
      \end{itemize}
    %\end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item 
    \end{itemize}
  \end{block}
\end{frame}

@@

\section{References}

%\begin{frame}{References}
%  \bibliographystyle{IEEEtran}
%   \begin{itemize}
%     \item N. Rawashdeh, R. Haddad, O. Jadallah, and A. To’ma, “A person-following
% robotic cart controlled via a smartphone application: design and evaluation,”
% 09 2017, pp. 1–5.
%     \item M. M. Islam, A. Lam, H. Fukuda, Y. Kobayashi, and Y. Kuno, “An intelligent
% shopping support robot: understanding shopping behavior from 2d skeleton data using gru network,” ROBOMECH Journal, vol. 6, no. 1, 2019.
%     \item J. Sales, J. Marti, R. Marin Prades, E. Cervera, and P. Sanz, “Comparob: The
% shopping cart assistance robot,” International Journal of Distributed Sensor Networks, vol. 2016, pp. 1–15, 02 2016.
%     \item M. S. Miah, J. Knoll, and K. Hevrdejs, “Intelligent range-only mapping and navigation for mobile robots,” IEEE Transactions on Industrial Informatics, vol. 14, no. 3, pp. 1164–1174, 2018.
%     \item D. Li and S. Lane, “A novel and versatile parabolic reflector that significantly
% improves wi-fi reception at different distances and angles,” 2013.

%   \end{itemize}

% \end{frame}

\begin{frame}[allowframebreaks]{References}

@@

%\begin{itemize}
%\item
%@INPROCEEDINGS{Donjaroennon2021,
%  author={Donjaroennon, Natthapon and Nuchkum, Suphatchakan and Leeton, Uthen},
%  booktitle={2021 9th International Electrical Engineering Congress (iEECON)}, 
%  title={Mathematical model construction of DC Motor by closed-loop system Identification technique Using Matlab/Simulink}, 
%  year={2021},
%  volume={},
%  number={},
%  pages={289-292},
%  doi={10.1109/iEECON51072.2021.9440305}}
%\end{itemize}
% 	\begin{itemize}
% 		\item T. Xie, H. Jiang, X. Zhao, and C. Zhang, “A wi-fi-based wireless indoor position sensing system with multipath interference mitigation,” Sep 2019. [Online].
% Available: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6767237/
% 		\item A. M. Ladd, K. E. Bekris, A. Rudys, L. E. Kavraki, and D. S. Wallach, “Robotics-
% based location sensing using wireless ethernet,” Wireless Networks, vol. 11, no. 1-2, p. 189–204, 2005.
% 		\item M. Lindhe, K. Johansson, and A. Bicchi, “An experimental study of exploiting multipath fading for robot communications,” Robotics: Science and Systems III, 2007.
% 		\item M. Lindhe and K. Johansson, “Using robot mobility to exploit multipath fading,”Wireless Communications, IEEE, vol. 16, pp. 30 – 37, 03 2009.
% 	\end{itemize}

>>>>

\begin{frame}{Introduction}{}
    \begin{block}{}
    	\begin{itemize}
    		\item Modeled
			\begin{itemize}
				\item Steering Subsystem
    				\item Acceleration Pedal Subsystem
    				\item Brake Pedal Subsystem
			\end{itemize}			    			
    		\item Not Modeled
			\begin{itemize}
				\item Shift Subsystem
    				\item Speed Subsystem
    				\item Speed Control Subsystem
			\end{itemize}			    			
    		\item Manual Data vs. By-Wire Data
    		\item Neural Network Modeling \cite{Zhou2019} \cite{matlabNeuralNet}
		\end{itemize}
    \end{block}

@@

\begin{frame}{Steering Subsystem}
	\begin{block}{}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item Only a few samples are just outside of the accuracy requirements
			\item Transfer function model did not meet the accuracy requirements
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}

@@

\begin{frame}{Acceleration Subsystem}
	\begin{block}{}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item All samples within 2\% of the actual output
			\item Transfer function model did not have the same accuracy bounds
			\item Fewer concerns about connections in Simulink
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Semester goals}
      \begin{itemize}
        \item Test our modeled subsystems on the HIL bench
        \item Collect data for the remaining subsystems
        \item Model the remaining subsystems and test on the HIL bench
        \item Create final report highlighting our findings
        \item Present our findings
      \end{itemize}
  \end{block}
  \begin{block}{Anticipated Challenges}
      \begin{itemize}
      	\item Having time to model the remaining subsystems
      	\item Needing to correct any models
      \end{itemize}
  \end{block}
\end{frame}

@@

\section{References}
\begin{frame}[allowframebreaks]{References}

@@
